\documentclass{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\title{CS 325: Project Scenario}
\author{Juliana, Diego, Adam}
\date{\today}

\begin{document}

\maketitle

\section*{Name}
\begin{center}
        \Huge{ManMoka}
\end{center}

\section*{Description}
\textbf{ManMoka} is an online and physical manga shop with a café. Its vast selection of Japanese comics and gourmet food and coffee provides customers with endless hours of entertainment. Membership provides customers with benefits such as renting mangas, credits for referring a member,



\section*{Questions}

\subsection*{General Questions}
\begin{itemize}
\item How many purchases has a customer made?
\item Who are the most profitable customers?
\item What are the best selling products?
\item What type of memberships? Cost?
\item When does a particular membership expire?
\item How can customers earn credits for referring new members?
\item How many members has a member referred?
\item How many store credits does a member have?
\item Are there any special events or themed nights at ManMoka?
\item Does ManMoka have multiple locations?
\item What days and hours is ManMoka open?
\item Are there any special deals for group events or gatherings?
\item How can customers provide feedback or suggestions to ManMoka?
\end{itemize}

\subsection*{Manga Questions}
\begin{itemize}
\item What genres of manga does ManMoka offer?
\item How many mangas are in each genre?
\item What are the most popular products? Genres?
\item How much does it cost to buy a manga? Rent?
\item What is a particular customer's favorite genre?
\item How does the manga rental service work for members?
\item Is there a limit to the number of mangas a customer can rent at once?
\item What's the late fee? damage fee?
\item May children access adult mangas?
\item How do I rent a manga?
\item When must a rental be returned?
\item Which mangas be rented?
\item Can customers purchase or rent manga online for delivery?
\item Does ManMoka offer any exclusive or limited edition manga?
\item How often does ManMoka receive new manga releases?
\item Are there any discounts or promotions?
\item Can customers request specific manga titles that are not currently in stock?
\item Can customers preorder unreleased mangas?
\item Does ManMoka host any manga-related workshops or classes?
\item Are there any quiet manga reading areas?
\end{itemize}

\subsection*{Cafe Questions}

\begin{itemize}
\item What type of gourmet food and drinks are available at the café?
\item Can customers reserve a table at the café in advance?
\item Are there gluten-free, vegetarian, vegan, or low-carb options?
\end{itemize}

\section*{Business Rules}

\begin{enumerate}
\item Rentals incur a late fee if not returned on time.
\item Members cannot rent while a rental is past due.
\item Members may only rent 10 mangas at a time.
\item Damage to a rental results in a fee.
\item Membership is limited to one person.
\item Minors may not rent adult mangas.
\item Give discounts to members who refer new customers.
\item Must provide analysis for profits, costs, assets, and liabilities.
\item Maintain a clean and inviting environment.
\item Update stock regularly to keep up with new releases.
\item Provide personalized recommendations based on customers' past purchases and preferences.
\item Ensure efficient and reliable shipping for online orders to meet customer expectations.
\item Implement a customer feedback system to gather insights and improve services.
\item Host manga-related events and activities to engage the community and attract new customers.
\item Collaborate with artists or creators for exclusive merchandise or events.
\item Manage inventory effectively to ensure popular titles are always in stock.
\item Develop partnerships with publishers or distributors to offer exclusive content.
\item Utilize social media and online marketing to reach a wider audience.
\item Create a customer loyalty program to reward frequent purchases and engagement.
\item Stay informed about industry trends and innovations to remain competitive in the market.
\end{enumerate}

\end{document}
