\documentclass{scrartcl}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\title{Business Rules}
\subtitle{CS 325 Database Design}
\author{Juliana, Diego, Adam}
\date{\today}

\begin{document}

\maketitle


\section*{Business Rules}

\begin{enumerate}
\item Rentals incur a late fee if not returned on time.
\item Members cannot rent while a rental is past due.
\item Members may only rent 10 mangas at a time.
\item Damage to a rental results in a fee.
\item Membership is limited to one person.
\item Minors may not rent adult mangas.
\item Give discounts to members who refer new customers.
\item Must provide analysis for profits, costs, assets, and liabilities.
\item Maintain a clean and inviting environment.
\item Update stock regularly to keep up with new releases.
\item Provide personalized recommendations based on customers' past purchases and preferences.
\item Ensure efficient and reliable shipping for online orders to meet customer expectations.
\item Implement a customer feedback system to gather insights and improve services.
\item Host manga-related events and activities to engage the community and attract new customers.
\item Collaborate with artists or creators for exclusive merchandise or events.
\item Manage inventory effectively to ensure popular titles are always in stock.
\item Develop partnerships with publishers or distributors to offer exclusive content.
\item Utilize social media and online marketing to reach a wider audience.
\item Create a customer loyalty program to reward frequent purchases and engagement.
\item Stay informed about industry trends and innovations to remain competitive in the market.
\end{enumerate}
\end{document}
